---
title: "p8105_hw1_wd2311"
author: "wd2311"
date: "2025-09-21"
output: html_document
---

Loading packages
```{r}
library(dplyr)
library(ggplot2)
library(moderndive)
```


# Problem 1
### Load Data
Load the early_january_weather dataset from moderndive library
```{r}
data("early_january_weather")
```

### Quick description
This dataset has 358 rows and 15 columns.  
The variables include: origin, year, month, day, hour, temp, dewp, humid, 
wind_dir, wind_speed, wind_gust, precip, pressure, visib, time_hour  
The mean temperature is about 39.58212.
```{r}
weather <- early_january_weather
names(weather)
nrow(weather)
ncol(weather)
mean(weather$temp, na.rm = TRUE)
```
### Scatterplot
Temperature generally increase from beginning to the middle of the month, with 
demonstrating a daily pattern of dipping overnight and rising during daytime 
hours. Points with higher humidity tend to cluster around Jan 12 to Jan 13, with
lower daily temperature variation. 
```{r}
plot_temp_hour <-
  ggplot(weather, aes(x = time_hour, y = temp, color = humid)) +
  scale_color_continuous(name = "Humidity (%)") +
  geom_point(alpha = 0.7, size = 1.8) +
  labs(
    x = "Time (hour)",
    y = "Temperature (°F)",
    title = "Early January Weather"
  ) +
  theme_minimal(base_size = 12)

plot_temp_hour
```


```{r}

```

```{r}

```


```{r}

```




```{r}

```


```{r}

```







