---
title: "p8105_hw1_wd2311"
author: "wd2311"
date: "2025-09-20"
output: html_document
---

Loading packages
```{r}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(moderndive)
```


# Problem 1
### Load Data
Load the early_january_weather dataset from moderndive library
```{r}
data("early_january_weather")
```

### Quick description
This dataset has 358 rows and 15 columns.  
The variables include: origin, year, month, day, hour, temp, dewp, humid, 
wind_dir, wind_speed, wind_gust, precip, pressure, visib, time_hour  
The mean temperature is about 39.58212.
```{r}
weather <- early_january_weather
names(weather)
nrow(weather)
ncol(weather)
mean(weather$temp, na.rm = TRUE)
```
### Scatterplot
Temperature generally increase from beginning to the middle of the month, except 
for a sudden drop at Jan 15. Also there is a daily pattern of dipping overnight 
and rising during daytime hours. Points with higher humidity tend to cluster 
around Jan 11 to Jan 14, with lower daily temperature variation. 
```{r}
plot_temp_hour <-
  ggplot(weather, aes(x = time_hour, y = temp, color = humid)) +
  scale_color_continuous(name = "Humidity (%)") +
  geom_point(alpha = 0.7, size = 1.8) +
  labs(
    x = "Time (hour)",
    y = "Temperature (°F)",
    title = "Early January Weather"
  ) +
  theme_minimal(base_size = 12)

plot_temp_hour
```

# Problem 2
### Create data fram
```{r}
problem2_df <- tibble(
  num_var   = rnorm(10),
  log_var   = num_var > 0,
  char_var  = letters[1:10],
  fact_var  = factor(rep(c("low", "med", "high"), length.out = 10))
)

problem2_df
```

### take the mean of each variable
```{r}
mean(df %>% pull(num_var))    # works: numeric mean
mean(df %>% pull(log_var))    # works: TRUE=1, FALSE=0
mean(df %>% pull(char_var))   # error: not numeric
mean(df %>% pull(fact_var))   # error: not numeric
```

### Convert to numeric and retry
```{r}
as.numeric(df$log_var)   
as.numeric(df$char_var)    
as.numeric(df$fact_var) 
```




```{r}

```


```{r}

```







